A Discontinuous Petrov-Galerkin method for compressible flow problems

### 2012-08-14 docs/Jesse/Proposal/boeingPres.tex
last mods to boeing pres

\frame{
\frametitle{Additional examples}
\begin{figure}
\centering
\subfigure[Advection skew]{
\includegraphics[scale = .175]{figs/Conservative/hughes.png}
}
\subfigure[Flow over a step]{
\includegraphics[scale = .175]{figs/Conservative/step.png}
}
\subfigure[Double glazing]{
\includegraphics[scale = .182]{figs/Conservative/doubleGlazing.png}
}
\end{figure}
Locally conservative version of DPG performs very similarly to the standard DPG in all cases.
}

@@

\begin{figure}
\centering
\subfigure{
\includegraphics[scale = .225]{figs/Conservative/Hemker/WithoutMesh.png}
}
\subfigure{
\includegraphics[scale = .225]{figs/Conservative/Hemker/WithMesh.png}
}
\caption{Convection-diffusion solution to the Hemker problem.}
\end{figure}
}
\frame{
\frametitle{Current work - high-lift airfoil}
\begin{figure}
\centering
\subfigure{
\includegraphics[scale = .1875]{figs/Conservative/Airfoil-Conservative-1E-3/solution.png}
}
\subfigure{
\includegraphics[scale = .175]{figs/Conservative/Airfoil-Conservative-1E-3/mesh7.png}
}
\caption{Convection-diffusion solution over the high-lift airfoil, with advection at an angle, $\epsilon = 1e-3$, with $p=3$. Mesh is generated by \emph{Triangle}.}
\end{figure}
}

>>>>

\frame{
\frametitle{Additional examples}
\begin{figure}
\centering
\subfigure[Advection skew]{
\includegraphics[scale = .175]{figs/Conservative/hughes.png}
}
\subfigure[Flow over a step]{
\includegraphics[scale = .175]{figs/Conservative/step.png}
}
\subfigure[Double glazing]{
\includegraphics[scale = .182]{figs/Conservative/doubleGlazing.png}
}
\end{figure}
Locally conservative version of DPG performs very similarly to the standard DPG in all cases over a range of $\epsilon$. 
}

@@

\begin{figure}
\centering
\subfigure{
\includegraphics[scale = .225]{figs/Conservative/Hemker/WithoutMesh.png}
}
\subfigure{
\includegraphics[scale = .225]{figs/Conservative/Hemker/WithMesh.png}
}
\caption{Convection-diffusion solution to flow over a cylinder at $\epsilon = 1e-4$.}
\end{figure}
}
\frame{
\frametitle{Current work - high-lift airfoil}
\begin{figure}
\centering
\subfigure{
\includegraphics[scale = .1875]{figs/Conservative/Airfoil-Conservative-1E-3/solution.png}
}
\subfigure{
\includegraphics[scale = .175]{figs/Conservative/Airfoil-Conservative-1E-3/mesh7.png}
}
\caption{Convection-diffusion solution over the high-lift airfoil, with advection at an angle, $\epsilon = 1e-3$, with $p=3$. Mesh is generated by \emph{Triangle}.}
\end{figure}
}
